Accessible, realistic genome simulation with selection using \stdpopsim

### 2025-03-17 analysis2_manuscript.tex
edits to affiliations

\author[4]{Ornob Alam}
\author[5]{Maria Izabel A. Cavassim}
\author[6]{Peter D. Fields}
\author[7]{Benjamin C. Haller}
\author[8,9]{Xin Huang}
\author[10]{Ben Jeffrey}
\author[5]{Christopher C. Kyriazis}
\author[2]{Kevin Korfmann}
\author[2]{Jiseon Min}
\author[2]{Chris C. R. Smith}

\author[2]{Scott T. Small}
\author[2]{Clara T. Rehmann}
\author[11]{Inés Rebollo}
\author[10]{Yan Wong}
\author[12]{Gregor Gorjanc}
\author[13]{Christian D. Huber}
\author[]{Yu Zhang}

\author[3]{Ryan N. Gutenkunst}
\author[10]{Jerome Kelleher}
\author[5]{Kirk E. Lohmueller}
\author[14]{Aaron P. Ragsdale}
\author[15]{Daniel R. Schrider}
\author[16]{Ilan Gronau}
\author[2,17]{Peter L. Ralph}
\author[2]{Andrew D. Kern}

\affil[*]{\small{These authors contributed equally to the paper.}}
\affil[1]{\small{Section for Molecular Ecology and Evolution, Globe Institute, University of Copenhagen, Denmark}}
\affil[2]{\small{Institute of Ecology and Evolution, University of Oregon, Eugene OR 97402, USA}}
\affil[3]{\small{Department of Molecular and Cellular Biology, University of Arizona, Tucson, AZ 85721, USA}}
\affil[4]{\small{Center for Systems Biology, New York University, New York NY, 10012 USA}}
\affil[5]{\small{Department of Ecology and Evolutionary Biology, University of California, Los Angeles, Los Angeles CA, USA}}
\affil[6]{\small{The Jackson Laboratory, Bar Harbor, ME, 04609 USA}}
\affil[7]{\small{Department of Computational Biology, Cornell University, Ithaca NY, USA}}
\affil[8]{\small{Department of Evolutionary Anthropology, University of Vienna, Vienna, Austria}}
\affil[9]{\small{Human Evolution and Archaeological Sciences (HEAS), University of Vienna, Vienna, Austria}}
\affil[10]{\small{Big Data Institute, Li Ka Shing Centre for Health Information and Discovery, University of Oxford, Oxford OX3 7LF, UK}}
\affil[11]{\small{Instituto Nacional de Investigación Agropecuaria (INIA), Estación Experimental Las Brujas, Ruta 48 km 10, Canelones, Uruguay}}
\affil[12]{\small{The Roslin Institute and Royal (Dick) School of Veterinary Studies, University of Edinburgh, Edinburgh EH25 9RG, UK}}
\affil[13]{\small{Department of Biology, Pennsylvania State University, University Park, PA 16802, USA}}
\affil[14]{\small{Department of Integrative Biology, University of Wisconsin-Madison, Madison WI, USA}}
\affil[15]{\small{Department of Genetics, University of North Carolina at Chapel Hill, Chapel Hill NC 27599, USA}}
\affil[16]{\small{Efi Arazi School of Computer Science, Reichman University, Herzliya, Israel}}
\affil[17]{\small{Department of Data Science, University of Oregon, Eugene OR 97402, USA}}

>>>>

\author[4]{Ornob Alam}
\author[5]{Maria Izabel A. Cavassim}
\author[6]{Peter D. Fields}
\author[7]{Benjamin C. Haller}
\author[8,9]{Xin Huang}
\author[10]{Ben Jeffrey}
\author[5]{Christopher C. Kyriazis}
\author[2]{Kevin Korfmann}
\author[2]{Jiseon Min}
\author[11]{Inés Rebollo}
\author[2]{Clara T. Rehmann}
\author[2]{Chris C. R. Smith}
\author[2]{Scott T. Small}
\author[12]{Georgia Tsambos}

\author[10]{Yan Wong}
\author[13]{Gregor Gorjanc}
\author[14]{Christian D. Huber}
\author[13]{Yu Zhang}

\author[3]{Ryan N. Gutenkunst}
\author[10]{Jerome Kelleher}
\author[5]{Kirk E. Lohmueller}
\author[15]{Aaron P. Ragsdale}
\author[16]{Daniel R. Schrider}
\author[17]{Ilan Gronau}
\author[2,18]{Peter L. Ralph}
\author[2]{Andrew D. Kern}

\affil[*]{\small{These authors contributed equally to the paper.}}
\affil[1]{\small{Section for Molecular Ecology and Evolution, Globe Institute, University of Copenhagen, Denmark}}
\affil[2]{\small{Institute of Ecology and Evolution, University of Oregon, Eugene OR 97402, USA}}
\affil[3]{\small{Department of Molecular and Cellular Biology, University of Arizona, Tucson, AZ 85721, USA}}
\affil[4]{\small{Center for Systems Biology, New York University, New York NY, 10012 USA}}
\affil[5]{\small{Department of Ecology and Evolutionary Biology, University of California, Los Angeles, Los Angeles CA, USA}}
\affil[6]{\small{The Jackson Laboratory, Bar Harbor, ME, 04609 USA}}
\affil[7]{\small{Department of Computational Biology, Cornell University, Ithaca NY, USA}}
\affil[8]{\small{Department of Evolutionary Anthropology, University of Vienna, Vienna, Austria}}
\affil[9]{\small{Human Evolution and Archaeological Sciences (HEAS), University of Vienna, Vienna, Austria}}
\affil[10]{\small{Big Data Institute, Li Ka Shing Centre for Health Information and Discovery, University of Oxford, Oxford OX3 7LF, UK}}
\affil[11]{\small{Instituto Nacional de Investigación Agropecuaria (INIA), Estación Experimental Las Brujas, Ruta 48 km 10, Canelones, Uruguay}}
\affil[12]{\small{Department of Genome Sciences, University of Washington, Seattle WA, USA}}
\affil[13]{\small{The Roslin Institute and Royal (Dick) School of Veterinary Studies, University of Edinburgh, Edinburgh EH25 9RG, UK}}
\affil[14]{\small{Department of Biology, Pennsylvania State University, University Park, PA 16802, USA}}
\affil[15]{\small{Department of Integrative Biology, University of Wisconsin-Madison, Madison WI, USA}}
\affil[16]{\small{Department of Genetics, University of North Carolina at Chapel Hill, Chapel Hill NC 27599, USA}}
\affil[17]{\small{Efi Arazi School of Computer Science, Reichman University, Herzliya, Israel}}
\affil[18]{\small{Department of Data Science, University of Oregon, Eugene OR 97402, USA}}
